Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-07-30 writing/nips_submission/response/EML_response.tex
Tweaks

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet-50 as the input encoder, we achieved test accuracy of 61.0\% on 5-shot, 5-way classification, competitive with e.g. MAML. We expect that with more than a few days to tune hyperparameters and train larger models we could do much better. \par

>>>>

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 61.0\% on 5-shot, 5-way classification, competitive with e.g. MAML. We expect that with more than a few days to tune hyperparameters and refine the model we could do much better. \par
